\documentclass[letterpaper,10pt]{article}

\usepackage[margin=1.5in]{geometry}

\usepackage[x11names]{xcolor}
\usepackage[colorlinks=true,urlcolor=SteelBlue4]{hyperref}

\usepackage{titlesec}
\titleformat{\section}[hang]{\sc\Large}{}{0pt}{}
\titlespacing{\section}{0pt}{2.5em}{1em}
\titleformat{\subsection}[runin]{\bf}{}{0pt}{}
\titlespacing{\subsection}{0pt}{1ex}{0pt}

\usepackage{enumitem}
\setlist[itemize]{itemsep=0ex,parsep=1ex,topsep=.8ex}

\setlength{\parindent}{0pt}


\begin{document}


\begin{center}
  \Large
  Curriculum Vitae:  Jonah Emery Bernhard \\[1ex]
  \normalsize\rm
  Department of Physics \\
  Duke University \\
  Durham, NC 27708 \\[1ex]
  \href{http://jbernhard.xyz}{\nolinkurl{jbernhard.xyz}} \\
  \href{https://github.com/jbernhard}{\nolinkurl{github/jbernhard}} \\
  \href{mailto:jonah.bernhard@gmail.com}{\nolinkurl{jonah.bernhard@gmail.com}}
\end{center}


\section{Education}


\subsection{Duke University}, Durham, North Carolina. \hfill August 2011--Present

\begin{itemize}
  \item Ph.D. Physics, expected 2016.
  \item Defended preliminary exam, \emph{QGP parameter extraction via a global analysis of event-by-event flow coefficient distributions}, January 2014.
\end{itemize}


\subsection{Swarthmore College}, Swarthmore, Pennsylvania. \hfill September 2007--May 2011

\begin{itemize}
  \item B.A.\ Chemical Physics with Highest Honors, 2011.
  \item Senior thesis:  \emph{Lorentz violation in solar-neutrino oscillations} \\
          Nominated for APS Apker Award.
\end{itemize}



\section{Research Experience}


\subsection{Graduate research assistant}, Duke University. \hfill January 2012--Present

\begin{itemize}
  \item Simulated event-by-event relativistic heavy-ion collisions on an unprecedented scale.
  \item Constrained fundamental quark-gluon plasma properties via systematic model-to-data comparison.
  \item Based preliminary exam on this work.
  \item Adviser:  Steffen Bass
\end{itemize}


\subsection{Undergraduate research assistant}, Swarthmore College. \hfill January 2010--May 2011

\begin{itemize}
  \item Modeled and quantified the possible effects of Lorentz violation on solar neutrinos.
  \item Based undergraduate thesis on this work.
  \item Adviser:  Matthew Mewes
\end{itemize}



\subsection{Summer research fellow}, Swarthmore College. \hfill June--August 2009

\begin{itemize}
  \item Performed experimental studies of the excited states of nitric oxide gas.
  \item Adviser:  Thomas Stephenson
\end{itemize}



\pagebreak



\section{Publications}

J.~E.~Bernhard, P.~W.~Marcy, C.~E.~Coleman-Smith, S.~Huzurbazar, R.~L.~Wolpert, and S.~A.~Bass,
\emph{Quantifying properties of hot and dense QCD matter through systematic model-to-data comparison},
\href{http://dx.doi.org/10.1103/PhysRevC.91.054910}{Phys.\ Rev.\ C {\bf 91}, 054910 (2015)},
\href{http://arxiv.org/abs/1502.00339}{arXiv:1502.00339 [nucl-th]}.

\vspace{1em}

J.~S.~Moreland, J.~E.~Bernhard, and S.~A.~Bass,
\emph{Alternative ansatz to wounded nucleon and binary collision scaling in high-energy nuclear collisions},
\href{http://dx.doi.org/10.1103/PhysRevC.92.011901}{Phys.\ Rev.\ C {\bf 92}, 011901 (2015)},
\href{http://arxiv.org/abs/1412.4708}{arXiv:1412.4708 [nucl-th]}.



\section{Presentations}


\subsection{Quark Matter 2015}, Kobe, Japan. \hfill September 29, 2015 \\
Poster: \emph{Bayesian characterization of the \\ initial state and QGP medium}

\subsection{Institute for Nuclear Theory workshop}, University of Washington. \hfill July 14, 2015 \\
\emph{Quantifying properties of hot and dense QCD matter \\ through systematic model-to-data comparison}

\subsection{2015 RHIC \& AGS users' meeting}, Brookhaven National Lab. \hfill June 9, 2015 \\
\emph{Bayesian methods for constraining initial conditions and viscosity}

\subsection{CIPANP 2015}, Vail, Colorado. \hfill May 22, 2015 \\
\emph{Quantifying properties of hot and dense QCD matter \\ through systematic model-to-data comparison}

\subsection{MADAI workshop}, Michigan State University. \hfill July 7, 2014 \\
\emph{Model-to-data comparison for event-by-event flow distributions: \\ progress and pitfalls}

\subsection{Quark Matter 2014}, Darmstadt, Germany. \hfill May 20, 2014 \\
Poster: \emph{QGP parameter extraction via a global \\ analysis of event-by-event flow coefficient distributions}

\subsection{ECT*}, Trento, Italy. \hfill May 13, 2014 \\
\emph{QGP parameter extraction via a global \\ analysis of event-by-event flow coefficient distributions}

\subsection{JET bulk group meeting}, Duke University. \hfill March 24, 2014 \\
\emph{QGP parameter extraction via a global analysis of \\ event-by-event flow coefficient distributions}

\subsection{DNP fall 2013 meeting}, Newport News, Virginia. \hfill October 26, 2013 \\
\emph{QGP parameter extraction via a global analysis of \\ event-by-event flow coefficient distributions}

\subsection{Sampling workshop}, Frankfurt, Germany. \hfill July 20, 2013 \\
\emph{QGP parameter extraction via a global analysis of \\ event-by-event flow coefficient distributions}

\subsection{Senior honors talk}, Swarthmore College. \hfill April 27, 2011 \\
\emph{Lorentz violation in solar-neutrino oscillations}

\subsection{CPT '10 meeting}, Indiana University. \hfill July 1, 2010 \\
Poster: \emph{Lorentz violation in solar-neutrino oscillations}



\section{Additional Academic Training}

\subsection{JET Summer School 2014}, University of California, Davis. \hfill June 19--21, 2014

\subsection{ECT* Doctoral Training Program}, Trento, Italy. \hfill April 7--May 16, 2014

\subsection{JET Summer School 2013}, Ohio State University. \hfill June 12--14, 2013



\section{Teaching Experience}

\subsection{Recitation instructor}, Duke University. \hfill August 2011--April 2013

\begin{itemize}
  \item Introductory Mechanics
  \item Introductory Electricity \& Magnetism
\end{itemize}


\subsection{Teaching assistant}, Swarthmore College. \hfill September 2009--April 2011

\begin{itemize}
  \item Introductory Mechanics
  \item Introductory Electricity \& Magnetism
  \item Mathematical Methods of Physics
  \item Organic Chemistry
\end{itemize}



\end{document}
