% resume.tex
% created 04:41:22 PM on Saturday 09/18/10

\documentclass[letterpaper,10pt]{article}

\usepackage{fullpage}
%\usepackage[letterpaper]{geometry}
\usepackage[version=3]{mhchem}

\pagestyle{empty}
\setlength{\parindent}{0px}

\linespread{1.13}


\newcommand{\heading}[1]{\medskip\bigskip \textsc{#1} \medskip \hrule \smallskip}
\newcommand{\notyet}{$^{\dagger\hspace{2px}}$}


\begin{document}


\Large{Jonah Bernhard} \hfill \normalsize{jonah.bernhard@gmail.com} \\[4pt]
203 Broadstreet Hollow \hfill cell: (845) 332-0317 \\
Shandaken, NY 12480 \hfill home: (845) 688-7148

\medskip

\heading{Education}
\medskip
Swarthmore College, Swarthmore, PA \hfill September 2007 -- present \\[2pt]
Expected graduation date:  June 2011
\begin{itemize}
  \item Honors Major in Chemical Physics
    \begin{description}
      \item[GPA:] 3.60
      \item[Key Courses:]  Classical Mechanics, Electrodynamics, Quantum Theory, Statistical Mechanics, \\ General Relativity,\notyet Physical Chemistry, 
        Quantum Chemistry and Spectroscopy\notyet
      \item[Honors Research Thesis:]  {\em Lorentz violation in solar-neutrino oscillations} \\
        Adviser:  Matthew Mewes
    \end{description}
\end{itemize}
\footnotesize{$\dagger$: Will be taken during the Spring 2011 semester.} \normalsize

\smallskip\smallskip

\heading{Research Experience}
\begin{itemize}
  \item {\em Excited states of nitric oxide}\ \ (Experimental Physical Chemistry) \hfill May -- August 2009
    \begin{itemize}
      \item Received summer fellowship to study with Thomas Stephenson at Swarthmore College.
      \item Studied gas-phase collisions of nitric oxide with oxygen and nitrogen.
    \end{itemize}

  \item {\em Lorentz violation in solar-neutrino oscillations}\ \ (Theoretical Physics) \hfill January 2010 -- present
    \begin{itemize}
      \item Conducted at Swarthmore College with Matthew Mewes during the academic year and as a summer fellowship.
      \item Modeled and studied the implications of possible Lorentz violation observed in solar neutrinos.
      \item Based senior thesis on research.
      \item Attended Fifth Meeting on CPT and Lorentz Symmetry at Indiana University and presented a poster.
    \end{itemize}
\end{itemize}


\heading{Teaching Experience}
\begin{itemize}
  \item Physics and Chemistry Mentor \hfill January 2009 -- present %\\[5pt] 
    \begin{itemize}
      \item Taught student help sessions for first and second-semester Organic Chemistry and General Physics classes at Swarthmore College.
    \end{itemize}
\end{itemize}


\heading{Computer Skills}
\begin{itemize}
  \item Extensive experience with Mathematica
  \item Familiarity with Matlab and LabView
  \item Freelance web design including server languages: HTML, CSS, PHP
  \item Python; UNIX shell scripts
\end{itemize}



\end{document}
